Synergistic retrievals of ice in clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-05-04 RST/responseReviewer2.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\author{Mircea Grecu and John E. Yorks}
\title{Response to Reviewers}
\date{}
\begin{document}
\maketitle
\textit{ \textbf{General Summary:}
This a well-written paper that fits within the scope of Journal of Atmospheric and 
Oceanic Technology and presents important and exciting results. The authors construct
 profiles of ice clouds based on CloudSat observations and then simulate retrievals 
 based on the instruments of the planned AOS mission. There are, however, 
 a few important ways in which the paper could be strengthened. I recommend 
 publication after the following comments are addressed.}\\
 We thank the reviewer for their perspective and constructive suggestions. Our point by point response is 
 provided below.\\
\textit{\textbf{Major Comments:} 1) There are several large sources of uncertainty that will be present in real 
retrievals from AOS that are ignored in this paper. While there is certainly still 
value in such analysis, it needs to be made more clear in the paper that this is an 
idealized scenario, and there should be more discussion about the sources of 
uncertainty that will affect real-world retrievals. Several in particular stand 
out to me. For one, it appears that all of the simulated measurements have been 
created at the same resolution (presumably, the resolution of CloudSat). This
should be clarified, and the authors should discuss how the lidar, radar, and 
radiometer will all have different resolutions and how this might affect results. 
Second, the electromagnetic scattering properties assumed in this study are 
unlikely to perfectly match reality. Finally, it appears that no measurement 
uncertainty has been assumed. The last paragraph of the paper does briefly mention 
many of these uncertainties, but they need to be introduced earlier in the 
manuscript, and more details are needed about the specifics of how IMPACTS
will help mitigate them.}\\
We thank the reviewer for the uncertainty discussion. Yes, indeed the resolution of the simulated 
observations is that of the CloudSat, while the AOS instruments are expected to have different resolutions,
which might impact results. In the revised manuscript, we included statements to convey this aspect.
We agree that the assumed electromagnetic scattering properties assumed in the study although
reasonable may contain significant uncertainties.  We acknowledge this aspect in the revised manuscript 
as well. Regarding the measurement uncertainties, we account for them in the radar and radiometer simulations,
but only in a highly idealized way in the lidar simulations.  Specifically, we assume random errors with 0.0 mean
and 0.5dB standard deviation in the radar observations \cite{takahashi2008}, and a Noise-Equivalent-Delta-T (NEDT)
of 1K, which is a readily achievable level for modern satellite radiometer \cite{draper2015}. A complex 
model of space-borne lidar measurement uncertainties was developed in \cite{liu2006}, but its parameters are
difficult to reliably quantify from theoretical considerations based on instrument expectations alone. Instead, we
assume a simple multiplicative error model, with the multiplicative factor model as a log-normally distributed random
variable with 0.0 mean and 1.0 standard deviation, which result in observation uncertainties similar to those in
the radar observations. We acknowledge the limitations of this model in the manuscript.\\
\textit{2) You say in your abstract (and conclusion) that “the characteristics of 
the instruments e.g.,  frequencies, sensitivities, etc. are set based on the 
expected characteristics of the AOS mission.” However, the AOS mission 
specifications are still very much in flux. Therefore, for reproducibility, 
I suggest adding a table explicitly laying out the frequencies and 
sensitivities you assume for each instrument (radar, lidar, radiometer). 
Some of these (e.g., the radiometer frequencies) are mentioned in the text, 
but it would be nice to see it all in one place.}\\
We agree with the reviewer that, unfortunately, the AOS mission is still in flux. We added a table in the revised
manuscript to summarize the assumed instrument characteristics.\\
\textit{\textbf{Minor Comments}
Line 38: Where is 8.0 dBZ coming from? There should be a citation here, or it should be stated that this is 
an estimate of the radar’s expected sensitivity.}\\
This is an estimate of the radar’s expected sensitivity provided by Japan Aerospace Exploration Agency (JAXA), which the AOS International
partner contributing the Ku-band radar in the inclined orbit.\\
\textit{Lines 50-51: While your approach is justifiable and worthwhile, it is worth noting that your CloudSat IWC retrieval 
also makes numerous assumptions about ice cloud microphysical properties and structures (as laid out in Section 2a). 
So the problem is not entirely avoided by relying on “observations” instead of models, as the observations were of 
radar reflectivity, not of ice water contents or particle sizes.}\\
We agree. We do not consider CloudSat retrievals uncertainties or bias free, but we prefer them because
they are consistent with an observed vertical distribution of reflectivity at W-band. The vertical distributions of radar reflectivity
derived from satellite or ground-based observations are generally difficult to reproduce by model simulations. We added a statement 
to this effect in the revised manuscript.\\
\textit{Lines 65-67: This is fine, but it should be noted that in doing this, you are underestimating the true retrieval 
uncertainty. The particle distribution assumptions and electromagnetic scattering properties that you use in training 
the retrieval algorithm will almost certainly not perfectly reflect the actual size and shape distributions of ice 
particles around the globe.}\\
We agree. As explained above, our  objective was to derive IWC distributions consistent with the observed vertical distribution of
CloudSat reflectivity, without implying that the resulting distributions are uncertainty or bias free.  To make the performance
assessment more realistic, in the revised version of the manuscript, we perturbed the $N_w$ value (which in the initial version was
parametrized as a function of height) used in the derivation of IWC as a function of observed CloudSat reflectivity by a random log-normally
distributed factor. This accounts for uncertainties in the PSDs (at least from the perspective of the normalized PSD framework) and 
makes the evaluation realistic. Nevertheless, as observed by the reviewer, the electromagnetic scattering properties are 
an additional source of uncertainty.  We included additional statements in the manuscript to describe $N_w$ perturbation approach and
discuss uncertainties in the electromagnetic scattering properties that are not quantified in the manuscript.\\ 
\textit{Lines 83-90 and Eq. (1): I looked over the Testud et al. (2001) paper, and could not find anything that directly
 supported this statement, or any equations that resembled Eq. (1). Please add further explanation, either here 
 or in an appendix, to help the reader follow your logic.}\\
We apologize for the confusion. Testud et al. (2001) only show that normalization by $N_w$ ($N_0^*$ in their notation) explains the variability
in Z-R relationships (fig. 9d). Ferreira et al. (2001) \cite{ferreira2001} make the more general statement that any two integrated rainfall parameters ($X$, $Y$) 
may be related through a power law of the form $X = m N_w^{(1-n)} X^n$, where $m$ and $n$ are constants almost independent of $N_w$. Delanoe et al. (2014)
 \cite{delanoe2014} show that the same relationship holds for ice PSDs. We added statements to this effect in the revised manuscript.\\
\textit{Figure 2: Neither the caption nor the text adequately explains what is being plotted in this figure. What does each 
individual point represent? The text says, “Figure 2 is a scatter plot representation of the class multiplicative 
coefficient ai as a function of relative height,” but if that were the case, I would expect there to be many more 
points on the scatter plot (i.e. 18 classes times a certain number of relative height levels, to yield hundreds of points).}\\
We apologize for the confusion.  The points in figure 2 were derived from 36 classes.  We initially used 36 classes in the analysis, but
we reduced the number of classes to 18 to make the classification and the Ensemble Kalman Filter more robust.  However, we kept the results from the
36 classes in the $N_w$ parameterization because they enable a more accurate representation of the variability of the multiplicative coefficient.
For each of the 36 classes, we regressed IWC from the 2C-ICE product against the observed CloudSat reflectivity and derived height of the associated
mean IWC profile peak.  We then plotted the multiplicative coefficient as a function of the height of the mean IWC profile peak.  The height was
evaluated relative to the freezing level.  We included clarifying statements in the manuscript.\\
\textit{Lines 120-121: How is the data in Fig. 2 used to parameterize Nw as a function of height? Do you fit a line/curve to the 
data in Fig. 2? This needs to be clarified.}\\
Yes, We fit a line to determine the variation of $ln(a)$ as a function of height and then divide the slope by $(1-b)$ to get the variation of
$ln(N_w)$ as a function of height.\\
\textit{Figure 3: It would be helpful to add vertical lines to these plots to indicate the detection thresholds you are 
assuming for the radar (8 dBZ?) and lidar.}\\
We included vertical lines to indicate the detection thresholds.\\
\textit{Line 220: It is my understanding that an ensemble Kalman smoother assumes normal distributions. How much does it matter 
that IWC is not normally distributed in nature?}\\
Yes, the ensemble Kalman smoother assumes normal distributions.  We derive a Kalman gain, i.e. a matrix of type $\mathbf{Cov(X,Y) Cov(Y,Y)^{-1}}$, 
for every class, and although IWC is not normally distributed in nature, its conditional class distributions are not likely to be as skewed 
as the entire distribution.
This is most likely why the Kalman smoother produces rather accurate results when observations from all instruments is available.  
Nevertheless, from the theoretical perspective, the Kalman Smoother results are suboptimal given the non-Gaussian distribution of IWC.  This
does not necessarily mean that more accurate results may be derived in practice given the multitude of uncertainty factors that may
impact the results.\\
\textbf{Typos}\textit{Line 276: “wells” should be “well”}\\
Thank you for pointing that out. We corrected it in the revised version of the manuscript.\\
\textit{Line 308: Figure 8 should be Figure 9}\\
Thank you for pointing that out. We corrected it in the revised version of the manuscript.\\
\textit{Line 315: IWP should be IWC}\\
Thank you for pointing that out. We corrected it in the revised version of the manuscript.\\
\textit{Line 361: eliminate “out}\\
Thank you for pointing that out. We corrected it in the revised version of the manuscript.\\
\pagebreak
\noindent \textbf{Reviewer 2:}\textit{The study investigates the synergy between observations from elastic backscatter lidar, Ku-band radar,
and sub-millimeter radiometer observations to retrieve ice concentrations. The topic is undoubtedly timely,
considering that AOS, NASA's upcoming satellite mission targeting remote sensing of the atmosphere,
is currently in its design phase. The methodology is sound, albeit slightly contrived. Methods and
results are presented in an accessible way.
Nonetheless, there are significant conceptual flaws in the study.}\\
We thank the reviewer for their perspective and constructive suggestions.\\

@@

\textit{10. l. 203: I don't think that 200 000 profiles can be considered a large dataset by today's standards.}\\
\newline
We agree that 200,000 profiles is not a large dataset by today's standards.  However, these profiles are derived from a month of CloudSat observations.
Specifically, all CloudSat and 2C-ICE product files from June 2019 were processed, and only profiles with no echo below the freezing level

@@

Thank you for pointing this out.  We added the missing word.\\
\newline

\begin{thebibliography}{999}

\bibitem{takahashi2008}
Takahashi N, Iguchi T. Characteristics of TRMM/PR system noise and their application to the rain detection algorithm. 
IEEE transactions on geoscience and remote sensing. 2008 May 16;46(6):1697-704.

\bibitem{draper2015}
Draper DW, Newell DA, Wentz FJ, Krimchansky S, Skofronick-Jackson GM. The global precipitation measurement (GPM) 
microwave imager (GMI): Instrument overview and early on-orbit performance. IEEE Journal of Selected Topics in 
Applied Earth Observations and Remote Sensing. 2015 Mar 2;8(7):3452-62.
\bibitem{liu2006}  
Liu Z, Hunt W, Vaughan M, Hostetler C, McGill M, Powell K, Winker D, and  Hu Y, 
Estimating random errors due to shot noise in backscatter lidar observations. 2006, Appl. Opt. 45, 4437-4447.

\bibitem{ferreira2001}
Ferreira, F., P. Amayenc, S. Oury, and J. Testud, 2001: Study and Tests of Improved Rain Estimates from the TRMM Precipitation Radar. 
J. Appl. Meteor. Climatol., 40, 1878–1899, https://doi.org/10.1175
